Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Fix grammar.
Clarify the description of testing modes.
These two testing modes are listed in this paragraph, as well as in the "Figures
8, 9, and 10" paragraph of section 5.2.2. I think the wording in the second case
was clearer, so I pulled it back and re-used it in the previous case.

Three tests were run at 10 different cluster sizes (odd cluster sizes
from 3 to 21 nodes): \emph{test/test\_up.js} and
\emph{test/test\_kill\_nodes.js} in kill one (leader) node and kill
half nodes. Each of these tests was run with three different Raft election
timeout values: 100ms, 500ms, 1000ms. The
\emph{test/test\_chat\_propagate.js} test was run at
11 different cluster sizes (odd cluster sizes from 1 to 21 nodes).
Each test mode and cluster size was run 7 times for a total of 707
test runs (3*10*7*3 + 11*7)

@@

\begin{enumerate}
\item Explore the use of alternate WebRTC transport modes for relaxing
    ordering constraints and delivery guarantees. Since the Raft
    protocol is tolerant of out-of-order and dropped messages, it is
    possible that Raft over WebRTC could be more efficient with one or
    both of these constraints relaxed.
\item Test the survivability of the cluster when the signaling server
    becomes completely unresponsive or very slow.
\item Explore models for dynamically adjusting Raft timeout values to
    account for changing network and browser conditions.
\item Explore models for dealing with the case where the cluster goes
    from two nodes down to one node. Can usefulness and availability
    be improved without sacrificing Raft safety constraints?
\item Test the system in more diverse network environments. Determine
    the reliability of establishing direct browser-to-browser
    communication.  Determine if corporate firewalls make this as
    difficult as some of the documentation and standards texts imply. %TODO/CITE
\item Perform quantitative and real-world testing to better
    characterize the performance, availability and scalability
    characteristics of the system.
\item Explore models for timing out and automatically removing nodes
    when they become unresponsive without needing to be notified by
    the signaling server that the nodes have disconnected.
\item Consider extensions to the Raft protocol that enable slow
    leaders to be proactively detected so that a more capable node
    (network, CPU, etc) can be elected. This would help address that
    background page/tag throttling of modern browsers.
\item Test larger scale deployments spanning larger and more diverse
    network domains. Determine the factors that affect scalability and
    characterize scaling limits.
\item Perform wider cross-browser testing including Internet Explorer
    and Opera.
\item Implement Raft log compaction and full client linearizability.
\item Explore models that allow for a combination of strict shared
    state and high performance bulk data such as media or object
    blobs. For example, the data with full consensus might contain
    hashes that to the refer to bulk data.
\item Implement a Node.js based Raft over WebRTC application. This
    would allow non-browser contexts to participate in the Raft
    cluster together with the browser clients. PeerJS issue \#103 must
    be resolved for this to be feasible \cite{peerjs:103}.
\item Explore a design where some nodes of the cluster are non-voting
    and are not counted as part of transaction commit quorum. However,
    these nodes would still be included in the log replication
    algorithm. One model this would enable would be a configuration
    where a small group of voting nodes serve as the hub for a larger
    group of non-voting nodes. This may enable higher scaling of the
    system. It also enables interesting applications such as a logging
    or backup nodes.
\end{enumerate}

>>>>

Three tests were run at 10 different cluster sizes (odd cluster sizes
from 3 to 21 nodes): \emph{test/test\_up.js} and
\emph{test/test\_kill\_nodes.js} in both modes (kill only leader and kill just
under half the nodes).
Each of these tests was run with three different Raft election
timeout values: 100ms, 500ms, 1000ms. The
\emph{test/test\_chat\_propagate.js} test was run at
11 different cluster sizes (odd cluster sizes from 1 to 21 nodes).
Each test mode and cluster size was run 7 times for a total of 707
test runs (3*10*7*3 + 11*7)

@@

\begin{enumerate}
\item Explore the use of alternate WebRTC transport modes for relaxing
    ordering constraints and delivery guarantees. Since the Raft
    protocol is tolerant of out-of-order and dropped messages, it is
    possible that Raft over WebRTC could be more efficient with one or
    both of these constraints relaxed.
\item Test the survivability of the cluster when the signaling server
    becomes completely unresponsive or very slow.
\item Explore models for dynamically adjusting Raft timeout values to
    account for changing network and browser conditions.
\item Explore models for dealing with the case where the cluster goes
    from two nodes down to one node. Can usefulness and availability
    be improved without sacrificing Raft safety constraints?
\item Test the system in more diverse network environments. Determine
    the reliability of establishing direct browser-to-browser
    communication.  Determine if corporate firewalls make this as
    difficult as some of the documentation and standards texts imply. %TODO/CITE
\item Perform quantitative and real-world testing to better
    characterize the performance, availability and scalability
    characteristics of the system.
\item Explore models for timing out and automatically removing nodes
    when they become unresponsive without needing to be notified by
    the signaling server that the nodes have disconnected.
\item Consider extensions to the Raft protocol that enable slow
    leaders to be proactively detected so that a more capable node
    (network, CPU, etc) can be elected. This would help address that
    background page/tag throttling of modern browsers.
\item Test larger scale deployments spanning larger and more diverse
    network domains. Determine the factors that affect scalability and
    characterize scaling limits.
\item Perform wider cross-browser testing including Internet Explorer
    and Opera.
\item Implement Raft log compaction and full client linearizability.
\item Explore models that allow for a combination of strict shared
    state and high performance bulk data such as media or object
    blobs. For example, the data with full consensus might contain
    hashes that refer to bulk data.
\item Implement a Node.js based Raft over WebRTC application. This
    would allow non-browser contexts to participate in the Raft
    cluster together with the browser clients. PeerJS issue \#103 must
    be resolved for this to be feasible \cite{peerjs:103}.
\item Explore a design where some nodes of the cluster are non-voting
    and are not counted as part of transaction commit quorum. However,
    these nodes would still be included in the log replication
    algorithm. One model this would enable would be a configuration
    where a small group of voting nodes serve as the hub for a larger
    group of non-voting nodes. This may enable higher scaling of the
    system. It also enables interesting applications such as a logging
    or backup nodes.
\end{enumerate}
